Patient-Specific Neural Field Modeling from Micro-Electrode Data

### 2010-07-26 ltx/data_paper/DataPaper.tex
completed X1 and X4 formulation

\subsection{Estimating Support For Connectivity Kernel}
Under the assumption that the sensors are not spatially band-limiting the spectral content of the field and the connectivity kernel is homogeneous, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations. The deterministic component of the spatial mapping between consecutive fields is due to the convolution of the connectivity kernel with the firing rates. Although the relationship between the field and the firing rate is nonlinear, the cross-correlation analysis still extracts meaningful results. This can be seen by considering the three operating regions of the sigmoid. When the mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed. Therefore, this will not contribute to the results. Within the active region the sigmoid can be approximated by a linear function between consecutive samples, given a sufficiently high sampling rate. Therefore, linear cross-correlation analysis is appropriate. When the sigmoid is in the saturated region, the correlation coefficients will be higher, but not provide a meaningful measure of the kernel weight or gain. Therefore, we can not estimate the gain for the kernel using cross-correlation analysis, but the spatial extent can still be inferred. The gain for the kernel will be inferred using the EM algorithm described below.

Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression. By averaging over time, the effect of the disturbance is reduced. The subplots of the figure show that the connectivity kernel exhibits local excitation with surround inhibition. The plot indicate the support for excitatory aspect of the kernel centred at the origin is -2 mm to 2 mm in the x direction and slightly wider in the y direction.

The assumption of homgeneity can be tested by performing the correlation analysis 
\begin{itemize}
	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
	\item it is difficult because of the nonlinear function
	\item 
\end{itemize}

@@

\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right] \\

@@

 \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]

>>>>

\subsection{Estimating Support For Connectivity Kernel}
Under the assumption that the sensors are not spatially band-limiting the spectral content of the field, the support for the connectivity kernel can be inferred by studying the spatial cross-correlation between consecutive observations of the neural field. The deterministic component of the spatial mapping between consecutive fields is determined by the connectivity kernel convolved with the firing rates. Although the relationship between the field and the firing rate is nonlinear, the cross-correlation analysis still extracts meaningful results. This can be seen by considering the three operating regions of the sigmoid. When the sigmoid is mean membrane voltage is below the active region of the sigmoid, the firing rate will be approximately zero and only very small spatial correlations will observed. Therefore, this will not contribute to the results. Within the active region the sigmoid can be approximated by a linear function between consecutive samples, given a sufficiently high sampling rate. Therefore, linear cross-correlation analysis is appropriate. When the sigmoid is in the saturated region, the correlation coefficients will be higher. Therefore, we can not estimate the gain for the kernel, but the spatial extent can still be inferred. The gain for the kernel will be inferred using the EM algorithm described below.

Figure~\ref{fig:SpatialCrossCorrelation} shows the average (across time) cross-correlations between consecutive field observations for the different time periods relative to the seizure progression. By averaging over time, the effect of the disturbance on the analysis is reduced. The figure shows that the connectivity kernel has a local excitation with surround inhibition structure. can be approximated by a local as a two-dimensional Gaussian. The wi
\begin{itemize}
	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
	\item it is difficult because of the nonlinear function
	\item 
\end{itemize}

@@

\Xi_1&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t+1}^\top\right]=\sum_{t=1}^T\left(\mathbf M_t+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right) \\

@@

 \Xi_4&=\mathbf E_{(\theta',\xi')}\left[\sum_{t=1}^T\mathbf x_t\mathbf x_{t}^\top\right]=\sum_{t=1}^T\left(\mathbf P_t+\mathbf{\hat x}_t\mathbf{\hat x}_t^\top\right)
